The Place of the Local Group in the Cosmic Web

### 2014-07-25 paper/main.tex
updated paper body

@@

\begin{figure*}
\begin{center}
  \includegraphics[width=0.49\textwidth]{ELL_histogram_filament.pdf}
  \includegraphics[width=0.49\textwidth]{PROL_histogram_filament.pdf}
  \includegraphics[width=0.49\textwidth]{ELL_histogram_sheet.pdf}
  \includegraphics[width=0.49\textwidth]{PROL_histogram_sheet.pdf}
\end{center}
\caption{Cumulative distributions for the ellipticity and prolateness.
    \label{fig:ELL_PROL}}  
\end{figure*}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.49\textwidth]{ELL_delta_scatter.pdf}
  \includegraphics[width=0.49\textwidth]{PROL_delta_scatter.pdf}
\end{center}
\caption{Ellipticity and prolateness versus the overdensity for the pairs
in the general and $3\sigma$ samples. \label{fig:delta_ELL_PROL}} 
\end{figure*}

\begin{figure}
\begin{center}
  \includegraphics[width=0.50\textwidth]{density_histogram.pdf}
\end{center}
\caption{Overdensity distribution for the pairs in the three samples.
    \label{fig:density}}  
\end{figure}

>>>>

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{median_mass_fraction.pdf} 
\caption{Mass dependency of the fraction of pairs in the different
  environemnts.
\label{fig:median_fraction}}
\end{center}
\end{figure}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.31\textwidth]{median_mass_overdensity.pdf} 
  \includegraphics[width=0.32\textwidth]{median_mass_ellipticity.pdf} 
  \includegraphics[width=0.32\textwidth]{median_mass_prolateness.pdf} 
\caption{Mass dependency of the average dark matter overdensity (left),
  web ellipticity (middle) and web absolute value prolateness (right) at the
  pair location.
\label{fig:median_overdensity}}
\end{center}
\end{figure*}

\begin{figure}
\begin{center}
  \includegraphics[width=0.48\textwidth]{median_mass_alignment.pdf} 
\caption{Mass dependency of the median value for the dot product
  between the normal vector $\hat{n}$ and each one of the
  eigenvectors.  The lines show the trends for the general sample.
\label{fig:median_alignment_n}}
\end{center}
\end{figure}

@@

%\begin{figure*}
%\begin{center}
%  \includegraphics[width=0.49\textwidth]{ELL_histogram_filament.pdf}
%  \includegraphics[width=0.49\textwidth]{PROL_histogram_filament.pdf}
%  \includegraphics[width=0.49\textwidth]{ELL_histogram_sheet.pdf}
%  \includegraphics[width=0.49\textwidth]{PROL_histogram_sheet.pdf}
%\end{center}
%\caption{Cumulative distributions for the ellipticity and prolateness.
%    \label{fig:ELL_PROL}}  
%\end{figure*}

%\begin{figure*}
%\begin{center}
%  \includegraphics[width=0.49\textwidth]{ELL_delta_scatter.pdf}
%  \includegraphics[width=0.49\textwidth]{PROL_delta_scatter.pdf}
%\end{center}
%\caption{Ellipticity and prolateness versus the overdensity for the pairs
%in the general and $3\sigma$ samples. \label{fig:delta_ELL_PROL}} 
%\end{figure*}

%\begin{figure}
%\begin{center}
%  \includegraphics[width=0.50\textwidth]{density_histogram.pdf}
%\end{center}
%\caption{Overdensity distribution for the pairs in the three samples.
%    \label{fig:density}}  
%\end{figure}
